Pillar 2 - Topic Modeling

### 2019-04-04 Pillar 2 - Topic Modeling.Rmd
load d_text

For `d_text` we keep only the most recent year.
```{r import data, eval = TRUE}
#load
load("output/data_pillar_2.RDATA")

# keep most recent year
d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
```

@@

#Plot
plot_evaluation("overview")
plot_evaluation("manuals")
```

>>>>

For `d_text` we keep only the most recent year.
```{r import data, eval = TRUE}
#load
#load("output/data_pillar_2.RDATA")
load("./Output/d_text.RDATA")
```

@@

#Plot
plot_evaluation("catalogues")
plot_evaluation("manuals")
```
